---
title: "p8105_hw5_sy3269"
author: "Soomin You"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

For n people in a room, we will check for any duplicate birthdays. Some of the assumptions we make are as follows: 

1) there are at least two people share the same birthday 
2) there are no leap years 
3) birthdays are uniformly distributed over the year 


```{r}
bday_sim = function(n) {

  bdays = sample(1:365, size = n, replace = TRUE)
  
  duplicate = length(unique(bdays)) < n

  return(duplicate)
  
}
```


```{r}
sim_res = 
  expand_grid(
    n = 2:50,
    iter = 1:10000
  ) |> 
  mutate(res = map_lgl(n, bday_sim)) |> 
  group_by(n) |> 
  summarize(prob = mean(res))

sim_res |> 
  ggplot(aes(x = n, y = prob )) + 
  geom_line()
```

If the simulation is ran 10,000 times, we get a 


Next, run this function 10000 times for each group size between 2 and 50. For each group size, compute the probability that at least two people in the group will share a birthday by averaging across the 10000 simulation runs. Make a plot showing the probability as a function of group size, and comment on your results.

